 %use <pdflatex cv> to compile
\documentclass[]{article}% 
\usepackage[pdftex,%
bookmarks=true,%
bookmarksnumbered=false, % true means bookmarks in left window are numbered 
bookmarksopen=true, % true means only level 1  are displayed. 
colorlinks=true,%
citecolor=citegreen,% 
urlcolor=urlblue,% 
linkcolor=citeblue]{hyperref} 
\hypersetup{%
  pdftitle = {Curriculum Vitae of Nicholas G. Reich}, 
  pdfsubject = {Curriculum Vitae of Nicholas G. Reich}, 
  pdfkeywords = {pdf, hyperref, bookmarks, thumbnails}, 
  pdfauthor = {\textcopyright\ Heiko Oberdiek}, 
  pdfcreator = {\LaTeX\ with package \flqq hyperref\frqq}, 
  pdfproducer = {pdfeTeX-0.\the\pdftexversion\pdftexrevision}, }

\usepackage{amsmath,comment,fullpage,color}
\definecolor{citegreen}{rgb}{0, .75, 0} % less intense green 
\definecolor{citeblue}{rgb}{0.1, 0.1, 0.5} % less intense blue 
\definecolor{urlblue}{rgb}{0, 0, 0.5} % less intense red
\definecolor{webred}{rgb}{0.5, 0, 0}
\usepackage[margin=.8in]{geometry}

% \begin{center} \large \bf {} \pdfbookmark{}{}  \end{center}

\renewcommand{\familydefault}{cmss}
\newcommand{\spa}{\hspace{1cm} }
\newcommand{\tbf}{\textbf}

\newcommand{\ul}[1]{\underline{\smash{{#1}}}}

%% reverse enumerate
\usepackage{etaremune}

\begin{document}           
\fontsize{11}{13}  \selectfont

\begin{center} 
\Large CURRICULUM VITAE of Nicholas G. Reich \footnote{Last updated \today}
\end{center} 
\vspace*{11pt}

\begin{center} \large \pdfbookmark{CONTACT}{CONTACT} \bf CONTACT  \end{center}  

\noindent 
\hspace*{-.3cm}
\begin{tabular}{lp{5.2in}} 
 Lab website: & \href{https://reichlab.io/}{\url{https://reichlab.io}}\hfill \\
Email: & {\tt nick [at] umass.edu} \\ 
Mailing address: 
& Department of Biostatistics and Epidemiology \\
& University of Massachusetts - Amherst  \\
& School of Public Health and Health Sciences \\
 & 437 Arnold House, 715 North Pleasant Street \\
 & Amherst, MA 01003-9304 \\
GitHub: & \href{https://github.com/reichlab}{Reich Lab}, \href{https://github.com/nickreich}{personal} \\
Telephone: & (413) 545-4534 \\
\end{tabular} 

\vspace{.1in} 
\begin{center} \pdfbookmark{EDUCATION}{EDUCATION} \large \bf {EDUCATION} 
  \end{center}
  
\noindent Ph.D. in Biostatistics, Johns Hopkins Bloomberg School of Public Health, 2010\\
\hspace*{.7cm}  Thesis title: {\em Statistical methods for incomplete data from infectious disease outbreaks}\\
\hspace*{.7cm}  Thesis advisor: 
\href{http://works.bepress.com/rbrookmeyer/}{Ron Brookmeyer}
%\vspace{.1in} 
%\noindent Coursework in Biostatistics and Epidemiology, Boston University School of Public Health, 2004-2005.

\vspace{.1in} 
\noindent 
B.A. in English, Carleton College, 2001, {\em magna cum laude}




%\clearpage

\vspace{.2in} 
 \begin{center}
    \pdfbookmark{PROFESSIONAL}{PROFESSIONAL}
 	\large \bf {PROFESSIONAL EXPERIENCE}
  \end{center}

\noindent 
\begin{tabular}{p{1in}p{7in}}
2019 - 2020 & Visiting Faculty and Humboldt Research Fellow, Institut f\"ur Statistik, \\
& Ludwig-Maximilians-Universit\"at, Munich, Germany\\

2017 - & Associate Professor, Department of Biostatistics and Epidemiology\\ & University of Massachusetts, Amherst \\

2013 - 2017 & Assistant Professor, Department of Biostatistics and Epidemiology\\ & University of Massachusetts, Amherst \\

2011 - 2013 & Research Assistant Professor, Department of Biostatistics and Epidemiology\\ & University of Massachusetts, Amherst \\

2010 - 2011 & Post-doctoral fellow, Department of Epidemiology \& Department of Hospital  \\ & Epidemiology and Infection Control, Johns Hopkins University\\

2006 - 2010 & Research Assistant, Department of Biostatistics, Johns Hopkins University\\

2006 - 2008 & Statistical Consultant, Maryland League of Conservation Voters\\

2005 & Research Assistant, Framingham Heart Study, Boston, MA
\end{tabular}


\vspace{.1in} 
 \begin{center} 
    \pdfbookmark{HONORS AND AWARDS}{HONORS AND AWARDS} 
    \large \bf {HONORS AND AWARDS}
 \end{center}
\noindent
\begin{tabular}{lp{5.2in}}
2019 & Alexander von Humbolt Fellowship for Experienced Researchers  \\
2019 & Paper nominated for Shepard Science Award, CDC (Reich et al., 2018, {\em SciRep}) \\
2019 & Director's Award, 3rd year extension to funded DARPA Young Faculty Award \\ 
2019 & Nominated for College Outstanding Teacher Award, UMass-Amherst SPHHS \\
2015 & 1st place, Outstanding Research Articles in Biosurveillance, Int'l Soc of Disease Surveillance \\
2015 & Nominated for College Outstanding Teacher Award, UMass-Amherst SPHHS \\
2013 & Honorable Mention for coarseDataTools R package, \href{http://www.umass.edu/icb3/ossi}{Open Source Software Initiative} \\
2012 & Open Education Initiative Award, Provost's Office and Libraries at UMass-Amherst \\
2010 & Statistics in Epidemiology Young Investigator Award, ASA Stat in Epi. Section \\
2010 & First prize, Student Research Competition, APHA, Statistics Section  \\
2009 & \href{http://www.biostat.jhsph.edu/newsEvent/award/abbeyaward.shtml}{Helen Abbey Award} for excellence in teaching \\
& \hspace*{.7cm} Department of Biostatistics, Johns Hopkins School of Public Health\\
%2009 & Distinguished Student Paper Travel Award\\
%& \hspace*{.7cm}  International Biometric Society's Eastern North American Region\\
%2009 & Nominated for school-wide Teaching Assistant Recognition Award\\
%& \hspace*{.7cm}  Johns Hopkins School of Public Health\\ 
%2005 & National Institutes of Health Mental Health pre-Doctoral Training Grant \\
%2004 & Dean`s Scholar: Boston University School of Public Health \\ 
%2001 & Distinction for senior thesis ``Baseballs, Butterflies and Bloomsday: Chaos Theory in {\em Ulysses} and {\em Underworld}``: Carleton College English Dept \\%2001 & Margaret Dalton Curran award for senior thesis ``Baseballs, Butterflies and Bloomsday: Chaos Theory in {\em Ulysses} and {\em Underworld}``: Carleton College English Dept \\
%2001 & Distinction in English major: Carleton College\\
%2001 & Phi Beta Kappa\\
\end{tabular}

\vspace{.1in} 



%\clearpage

%\vspace{.2in} 
% \begin{center} 
%   \pdfbookmark{RESEARCH INTERESTS}{RESEARCH INTERESTS}  
%   \large \bf {RESEARCH INTERESTS}
% \end{center}

% \noindent {\em Infectious diseases}:  Statistial methods for modeling spatial-temporal dynamics of disease processes and for estimating natural history parameters of disease.\\
%{\em Missing or incomplete data}: Likelihood approaches, interval censoring, imputation. \\
%{\em Data visualization}: Telling stories with novel data displays. \\
%{\em Statistical computing}: Reproducible research. \\

\vspace{.2in} 
\begin{center} 
   \pdfbookmark{PUBLICATIONS}{PUBLICATIONS}  
   \large \bf {ORIGINAL RESEARCH} 
\end{center}


\hspace*{-.4cm}  \href{https://scholar.google.com/citations?user=AQUsdvkAAAAJ&hl=en}{Full citation list at Google Scholar} \\

\hspace*{-.4cm} {\bf Under review, under revision, or submitted}  \hfill {\footnotesize \_\_\_\_ = mentored student author}


\begin{etaremune}

\item \ul{Gibson GC}, Moran K, {\bf Reich NG}, Osthus D. Improving Probabilistic Infectious Disease Forecasting Through Coherence. [ \href{https://www.biorxiv.org/content/10.1101/2019.12.27.889212v1}{preprint} ] (to appear in {\em PLOS Comp Bio}) 


\item Ray EL, \ul{Wattanachit N}, Niemi J, \ul{Kanji AH}, \ul{House K}, \ul{Cramer EY}, Bracher J, Zheng A, Yamana TK, Xiong X, Woody S, Wang Y, Wang L, Walraven RL, Tomar V, Sherratt K, Sheldon D, Reiner RC, Prakash BA, Osthus D, Li ML, Lee EC, Koyluoglu U, Keskinocak P, Gu Y, Gu Q, George GE, España G, Corsetti S, Chhatwal J, Cavany S, Biegel H, Ben-Nun M, Walker J, Slayton R, Lopez V, Biggerstaff M, Johansson MA, {\bf Reich NG}, on behalf of the COVID-19 Forecast Hub Consortium. Ensemble Forecasts of Coronavirus Disease 2019 (COVID-19) in the U.S. [ \href{https://www.medrxiv.org/content/10.1101/2020.08.19.20177493v1}{preprint} ]

\item {\bf Reich NG}, \ul{Cornell M}, Ray EL, \ul{House K}, \ul{Le K}.
The Zoltar forecast archive:  a tool to facilitate standardization and storage of interdisciplinary prediction research. [\href{https://arxiv.org/abs/2006.03922}{preprint}]

\item Bracher J, Ray EL, Gneiting T, {\bf Reich NG}. 
Evaluating epidemic forecasts in an interval format.
[\href{https://arxiv.org/abs/2005.12881}{preprint}]

\item \ul{Lauer SA}, {\bf Reich NG}, Balzer LB. The covariate-adjusted residual estimator and its use in both randomized trials and observational settings. [ \href{https://arxiv.org/abs/1910.11397}{preprint} ]

\item \ul{McAndrew T}, {\bf Reich NG}. Adaptively stacking ensembles for influenza forecasting with incomplete data. [ \href{https://arxiv.org/abs/1908.01675}{preprint} ]

\item \ul{Kusiak C}, Santillana M, Lessler J, Iamsirithaworn S, {\bf Reich NG}. 
Real-time dengue forecasting in Thailand: a comparison of penalized regression approaches using internet search data.

% \item Whitcomb B, Madonna L, Roy A, {\bf Reich NG}, Bertone-Johnson E, Healy A. Inflammation during gestation; a longitudinal study of plasma cytokine measures in uncomplicated pregnancies.

%\item Althouse BM, Lessler J, {\bf Reich NG} Cummings DAT. Heterogeneous transmission in homogenous populations: over-dispersion arises endogenously from competitive interactions between transmitters.

%\hspace*{-.8cm} {\bf Accepted/in press}

\hspace*{-.8cm} {\bf Published}

\item Weinberger DM, Chen J, Cohen T, Crawford FW, Mostashari F, Olson D, Pitzer VE, {\bf Reich NG}, Russi M, Simonsen L, Watkins A, Viboud C. Estimation of Excess Deaths Associated With the COVID-19 Pandemic in the United States, March to May 2020. {\em JAMA Intern Med}. 2020. [ \href{https://jamanetwork.com/journals/jamainternalmedicine/fullarticle/2767980}{html} ]

\item Cummings DAT, Radonovich LJ, Gorse GJ, Gaydos CA, Bessesen MT, \ul{Brown AC}, Gibert CL, Hitchings MDT, Lessler J, Nyquist AC, Rattigan SM, Rodriguez-Barradas MC, Price CS, {\bf Reich NG}, Simberkoff MS, Perl TM. Risk Factors for Healthcare Personnel Infection with Endemic Coronaviruses (HKU1, OC43, NL63, 229E): Results from the Respiratory Protection Effectiveness Clinical Trial (ResPECT). {\em Clinical Infectious Diseases.} 2020. (in press) [ \href{https://doi.org/10.1093/cid/ciaa900}{html} ]

\item Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith H, Azman AS, {\bf Reich NG}, Lessler J. 
The incubation period of 2019-nCoV from publicly reported confirmed cases: estimation and application. 
{\em Annals of Internal Medicine}.
2020. 172(9):577-582. [ \href{https://doi.org/10.7326/M20-0504}{html} ]

\item Al Hossain F, Lover A, Corey G, {\bf Reich NG}, Rahman T. 
FluSense: A Contactless Sensing Platform for Patient Counts and Influenza-Like-Illness Surveillance in Hospital Waiting Areas.
{\em Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies}. 2020. 4(1): 1. [ \href{https://doi.org/10.1145/3381014}{html} ]

\item \ul{Brown AC}, \ul{Lauer SA}, Robinson CC, Nyquist AC, Rao S, {\bf Reich NG}.
Evaluating the ALERT algorithm for local outbreak onset detection in seasonal infectious disease surveillance data. {\em Stat Med}. 2020. 39(8):1145-1155. [ \href{https://onlinelibrary.wiley.com/doi/full/10.1002/sim.8467}{html} ; \href{https://www.biorxiv.org/content/10.1101/664433v1}{preprint} ]

\item {\bf Reich NG}, McGowan C, Yamana T, \ul{Tushar A}, Ray EL, Osthus D, Kandula S,  Brooks L,   \ul{Moore E}, \ul{Crawford-Crudell W},  \ul{Gibson GC}, \ul{Moore E}, \ul{Silva R}, Biggerstaff M, Johansson MA, Rosenfeld R, Shaman J. 
Accuracy of real-time multi-model ensemble forecasts for seasonal influenza in the U.S. {\em PLOS Comp Bio}. 2019. 15(11): e1007486. [ \href{https://doi.org/10.1371/journal.pcbi.1007486}{html} ; \href{https://www.biorxiv.org/content/10.1101/566604v1}{preprint} ]

\item Johansson MA, \dots, {\bf Reich NG}, \ul{Brown AC}, \ul{Lauer SA}, \ul{Ray EL}, \ul{Sakrejda K}, \ul{Meng X}, \dots  et al. Advancing probabilistic epidemic forecasting through an open challenge: The Dengue Forecasting Project. {\em PNAS}. 2019.  [ \href{https://www.pnas.org/content/pnas/early/2019/11/05/1909865116.full.pdf}{pdf} ; \href{https://doi.org/10.1073/pnas.1909865116}{html} ]

\item {\bf Reich NG}, Brooks L, Fox S, Kandula S, McGowan C, \ul{Moore E}, Osthus D, Ray EL, \ul{Tushar A}, Yamana T, Biggerstaff M, Johansson MA, Rosenfeld R, Shaman J. 
A collaborative multiyear, multimodel assessment of seasonal influenza forecasting in the United States {\em PNAS}. 2019. 116(8): 3146-3154.
[\href{https://www.biorxiv.org/content/early/2018/08/24/397190}{preprint} ; \href{https://doi.org/10.1073/pnas.1812594116}{html}]

\item Radonovich LJ, Simberkoff MS, Bessesen MT, \ul{Brown AC}, Cummings DAT, Gaydos C, Los J, Krosche AE, Gibert CL, Gorse GJ, Nyquist AC, {\bf Reich NG}, Rodriguez-Barradas MC, Price CS, Perl TM.
N95 Respirators vs Medical Masks for Preventing Influenza Among Health Care Personnel
A Randomized Clinical Trial. {\em JAMA}. 2019. 322(9): 824-833. [ \href{https://doi.org/10.1001/jama.2019.11645}{html} ]

\item McGowan C, Biggerstaff M, Johansson M, Apfeldorf K, Ben-Nun M, Brooks L, Convertino M, Erraguntla M, Farrow D, Freeze J, Ghosh S, Hyun S, Kandula S, Lega J, Liu Y, Michaud N, Morita H, Niemi J, Ramakrishnan N, \ul{Ray EL}, {\bf Reich NG}, Riley P, Shaman J, Tibshirani R, Vespignani A, Zhang Q, Reed C. Collaborative efforts to forecast seasonal influenza in the United States, 2015-2016. {\em Sci Rep}. 2019, 9(683). [ \href{https://www.nature.com/articles/s41598-018-36361-9}{html} ]
* {\bf Paper nominated for 2019 Shepard Science Award, CDC.}

\item \ul{Lauer SA}, \ul{Sakrejda K}, \ul{Ray EL}, Suangtho P, Hinjoy S, Iamsirithaworn S, Suthachana S, Cummings DAT, Lessler J, {\bf Reich NG}. Prospective forecasts of annual dengue hemorrhagic fever incidence in Thailand, 2010-2014. {\em PNAS}. 2018, 115(10) : E2175-E2182 [ \href{https://doi.org/10.1073/pnas.1714457115}{html} ] 

\item {\bf Reich NG}, Lessler J, Varma JK, Vora NM. Quantifying the Risk and Cost of Active Monitoring for Infectious Diseases.  {\em Nat Sci Rep}. 2018, 8: 1093. [ \href{https://doi.org/10.1038/s41598-018-19406-x}{html} ; \href{https://www.biorxiv.org/content/biorxiv/early/2017/06/28/156497.full.pdf}{preprint} ] \\ 
* {\bf Paper nominated for 2018 Shepard Science Award, CDC.}

\item \ul{Ray EL}, {\bf Reich NG}. Prediction of infectious disease epidemics via weighted density ensembles. {\em PLOS Comp Bio}. 2018, 14(2): e1005910. [ \href{https://doi.org/10.1371/journal.pcbi.1005910}{html} ; \href{https://arxiv.org/pdf/1703.10936.pdf}{preprint} ]

\item Frederick J, \ul{Brown AC}, Cummings DAT, Gaydos CA, Gibert CL, Gorse GJ, Los JG, Nyquist AC, Perl TM, Price CS, Radonovich LJ, {\bf Reich NG}, Rodriguez-Barradas MC, Bessesen MT, Simberkoff MS, for the ResPECT Team. Protecting Healthcare Personnel in Outpatient Settings: The Influence of Mandatory Versus Nonmandatory Influenza Vaccination Policies on Workplace Absenteeism During Multiple Respiratory Virus Seasons. {\em Infect Control Hosp Epidemiol}. 2018. [ \href{https://doi.org/10.1017/ice.2018.9}{html} ]

\item Wang X, {\bf Reich NG}, Horton N. Enriching Students' Conceptual Understanding of Confidence Intervals: An Interactive Trivia-based Classroom Activity. {\em American Statistician}. 2018. [ \href{https://arxiv.org/pdf/1701.08452.pdf}{preprint} ]

\item Freeman JR, Whitcomb BW, Roy A, Bertone-Johnson ER, {\bf Reich NG}, Healy AJ.
A pilot longitudinal study of anti-M\"ullerian hormone levels throughout gestation in low risk pregnancy.
{\em Health Science Reports}. 2018, e53.

\item \ul{Ray EL}, \ul{Sakrejda K}, \ul{Lauer SA}, Johansson MA, {\bf Reich NG}. Infectious disease prediction with kernel conditional density estimation. {\em Statistics in Medicine}. 2017. 36(30): 4908-4929. [ \href{http://onlinelibrary.wiley.com/doi/10.1002/sim.7488/full}{html}; \href{https://github.com/reichlab/article-disease-pred-with-kcde/raw/master/inst/article/infectious-disease-prediction-with-kcde.pdf}{preprint} ]

\item \ul{Tushar A}, {\bf Reich NG}. flusight: interactive visualizations for infectious disease forecasts.
{\em The Journal of Open Source Software}. 2017, 2(13). [ \href{http://dx.doi.org/10.21105/joss.00231}{html} ]

\item {\bf Reich NG}, \ul{Lauer SA}, \ul{Sakrejda K}, Iamsirithaworn S, Hinjoy S, Suangtho P, Suthachana S, Clapham H, Salje H, Cummings DAT, Lessler J. Challenges in real-time prediction of infectious disease: a case study of dengue in Thailand. {\em PLOS Neglected Tropical Diseases}. 2016, 10(6): e0004761. [
 \href{http://journals.plos.org/plosntds/article?id=10.1371/journal.pntd.0004761}{html}; \href{http://journals.plos.org/plosntds/article/asset?id=10.1371%2Fjournal.pntd.0004761.PDF}{pdf} ]

\item {\bf Reich NG}, Lessler J, \ul{Sakrejda K}, \ul{Lauer SA}, Iamsirithaworn S, Cummings DAT. Case studies in evaluating time series prediction models using the relative mean absolute error. {\em American Statistician}. 2016, 70(3):285-292. [ \href{http://www.tandfonline.com/doi/abs/10.1080/00031305.2016.1148631}{html}; \href{http://works.bepress.com/nicholas_reich/11}{pdf} ]

\item Lessler J, Ott CT, Carcelen AC, Konikoff JM, Williamson J, Bi Q, {\bf Reich NG}, Cummings DAT, Kucirka LM, Chaisson LH. Time to Key Events in the Course of Zika Infection and their Implications for Surveillance: A Systematic Review and Pooled Analysis. {\em Bulletin of the World Health Organization}. 2016, 94:841-849.  [ \href{http://www.who.int/bulletin/volumes/94/11/16-174540.pdf}{pdf} ]

\item Johansson MA, {\bf Reich NG}, Hota A, Brownstein JS, Santillana M.  Evaluating the performance of infectious disease forecasts: A comparison of climate-driven and seasonal dengue forecasts for Mexico. {\em Scientific Reports}. 2016, 6: 33707. [ \href{http://www.nature.com/articles/srep33707}{html} ; \href{http://www.nature.com/articles/srep33707.pdf}{pdf} ]

\item Radonovich LJ, Bessesen M, Cummings DAT, Eagan A, Gaydos C, Gibert C, Gorse G, Nyquist C, {\bf Reich NG}, Rodriguez-Barradas M, Savor-Price C, Shaffer R, Simberkoff M, Perl TM. The Respiratory Protection Effectiveness Clinical Trial (ResPECT):  A Cluster-Randomized Comparison of Respirator and Medical Mask Effectiveness against Respiratory Infections in Healthcare Personnel. {\em BMC Infectious Diseases}. 2016. 16:243. [ \href{http://bmcinfectdis.biomedcentral.com/articles/10.1186/s12879-016-1494-2}{html} ; \href{http://download.springer.com/static/pdf/373/art%253A10.1186%252Fs12879-016-1494-2.pdf?originUrl=http%3A%2F%2Fbmcinfectdis.biomedcentral.com%2Farticle%2F10.1186%2Fs12879-016-1494-2&token2=exp=1464985355~acl=%2Fstatic%2Fpdf%2F373%2Fart%25253A10.1186%25252Fs12879-016-1494-2.pdf*~hmac=9e94c59e60f042d33284a784b6a569770de1d589288d35b30ad76d47384ff900}{pdf} ]

\item Hart V, Sturgeon SR, {\bf Reich NG}, Sievert LL, Crawford SL, Gold EB, Avis NE, Reeves KW. Menopausal vasomotor symptoms and incident breast cancer risk in the Study of Women's Health Across the Nation. {\em Cancer Causes \& Control}. 2016, 27(11):1333-1340. [ \href{http://link.springer.com/article/10.1007/s10552-016-0811-9}{html} ] 

\item Silveira M, Wexler L, Chamberlain J, Straubaur KM, Spencer R, {\bf Reich NG}, Bertone-Johnson ER. Seasonality of Suicide Behavior in Northwest Alaska: 1990-2009. {\em Public Health}. 2016, 137: 35-43. [ \href{http://www.sciencedirect.com/science/article/pii/S0033350616000676}{html} ; \href{http://ac.els-cdn.com/S0033350616000676/1-s2.0-S0033350616000676-main.pdf?_tid=5cd5b858-29c9-11e6-8fa1-00000aab0f6b&acdnat=1464985730_b34086da82da5f671191a71700e8c7c8}{pdf} ]

\item {\bf Reich NG}, Cummings DAT, \ul{Lauer SA}, Zorn M, Robinson C, Nyquist AC, Price CS, Simberkoff M, Radonovich LJ, Perl TM. Triggering Interventions for Influenza: The ALERT Algorithm. {\em Clinical Infectious Diseases}. 2015, 60(4): 499--504. 
[\href{http://cid.oxfordjournals.org/content/60/4/499}{html} ; \href{http://cid.oxfordjournals.org/content/60/4/499.full.pdf+html}{pdf}]

\item \ul{Lauer SA}, Kleinman KP, {\bf Reich NG}. The Effect of Cluster Size Variability on Statistical Power in Cluster Randomized Trials. {\em PLoS ONE.} 2015, 10(4): e0119074 [ \href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0119074}{html} ; \href{http://www.plosone.org/article/fetchObject.action?uri=info:doi/10.1371/journal.pone.0119074&representation=PDF}{pdf} ]

\item Hart V, Reeves KW, Sturgeon SR, {\bf Reich NG}, Sievert LL, Kerlikowske K, Ma L, Shepherd J, Tice J, Sprague BL. The effect of weight change on volumetric measures of mammographic density. {\em Cancer Epidemiol Biomarkers Prev}. 2015, 24(4):761. [\href{http://cebp.aacrjournals.org/content/24/4/761.2.abstract}{html}]

\item Barney LE, Dandley EC, Jansen LE, {\bf Reich NG}, Mercurio AM, Peyton SR. Integrin Expression and Phenotype Predict Breast Cancer Metastasis. {\em Integrative Biology.} 2015, 7: 198-212. [\href{http://pubs.rsc.org/en/content/articlelanding/2015/IB/C4IB00218K#!divAbstract}{html} ; \href{http://pubs.rsc.org/en/content/articlepdf/2015/IB/C4IB00218K}{pdf}]

\item Elfawal M, Towler MJ, {\bf Reich NG}, Weathers PJ, Rich SM.  Dried whole plant Artemisia annua slows evolution of malaria drug resistance and overcomes resistance to artemisinin. {\em PNAS.} 2015, 112(3): 821--826. [\href{http://www.pnas.org/content/112/3/821.full.html}{html} ; \href{http://www.pnas.org/content/112/3/821.full.pdf}{pdf}] 

\item  Hart V, Reeves KW, Sturgeon SR, {\bf Reich NG}, Sievert LL, Kerlikowske K, Ma L, Shepherd J, Tice J, Mahmoudzadeh AP, Malkov S, Sprague BL. The effect of change in body mass index on volumetric measures of mammographic density. {\em Cancer Epi Biomarkers Prev}. 2015, 24:1724-1730. [\href{http://cebp.aacrjournals.org/content/early/2015/08/27/1055-9965.EPI-15-0330.short}{html} ; \href{http://cebp.aacrjournals.org/content/early/2015/08/27/1055-9965.EPI-15-0330.full.pdf+html}{pdf}]

%\hspace*{-.8cm} {\bf 2014}


%\hspace*{-.8cm} {\bf 2013}

\item {\bf Reich NG}, Shrestha S, King AA, Rohani P, Lessler J, Kalayanarooj S, Yoon IK, Gibbons RV, Burke DS, Cummings DAT. Interactions between serotypes of dengue highlight epidemiological impact of cross-immunity. {\em Journal of the Royal Society Interface}. 2013, 10 (86), 20130414. [\href{http://rsif.royalsocietypublishing.org/content/10/86/20130414.full}{html} ; \href{http://rsif.royalsocietypublishing.org/content/10/86/20130414.full.pdf}{pdf}]

\item Milstone AM, {\bf Reich NG}, Advani S, \ul{Yuan G}, Bryant K, Coffin SE, Huskins C, Livingston R, Saiman L, Smith PB, Song X. Catheter Dwell Time and CLABSIs in Neonates with PICCs: A Multicenter Cohort Study. {\em Pediatrics}. 2013, 132(6): 21609-e1615. [\href{http://pediatrics.aappublications.org/content/132/6/e1609.full}{html} ; \href{http://pediatrics.aappublications.org/content/132/6/e1609.full.pdf}{pdf}]

\item Lee RM, Lessler J, Lee RA, Rudolph KE, {\bf Reich NG}, Perl TM and Cummings DAT. Incubation periods of viral gastroenteritis: a systematic review. {\em BMC Infectious Diseases}. 2013, 13: 446. [\href{http://www.biomedcentral.com/1471-2334/13/446}{html} ; \href{http://www.biomedcentral.com/content/pdf/1471-2334-13-446.pdf}{pdf}]

\item Milstone AM, Elward A, Song X, Zerr DM, Orscheln R, Speck K, Obeng D, {\bf Reich NG}, Coffin SE, Perl TM for the Pediatric SCRUB Trial Study Group. Daily Chlorhexidine Bathing To Reduce Bacteremia in Critically Ill Children: a Multicenter, Cluster-Randomized, Two-Period Crossover Trial. {\em The Lancet}. 381 (9872), 1099-1106.
[\href{http://www.thelancet.com/journals/lancet/article/PIIS0140-6736(12)61687-0/fulltext}{html} ; \href{http://download.thelancet.com/pdfs/journals/lancet/PIIS0140673612616870.pdf}{pdf}]

\item Passaretti CL, Otter JA, {\bf Reich NG}, Myers JA, Shepard J, Howard T, Carroll KC, Lipsett P, Perl TM. Environmental decontamination with hydrogen peroxide vapor reduces the risk of patient acquisition of multidrug-resistant organisms. {\em Clinical Infectious Diseases}. 2013, 56(1): 27-35.
[\href{http://cid.oxfordjournals.org/content/56/1/27.full}{html} ; \href{http://cid.oxfordjournals.org/content/56/1/27.full.pdf+html}{pdf}]

\item Jumani K, Advani S, {\bf Reich NG}, Gosey L, Milstone AM. Complications Associated with Peripherally Inserted Central Venous Catheters in Children. {\em JAMA Pediatrics}. 2013, 167 (5): 429--435. [\href{http://archpedi.jamanetwork.com/article.aspx?articleid=1669324}{html} ; \href{http://www.jamanetwork.net/data/Journals/PEDS/926906/poa120082_429_435.pdf}{pdf}]

\item Xu G, Wesker J, White C, Campbell J, {\bf Reich NG}, Rich SM. Detection and heterogeneity of Borrelia burgdorferi in Ixodes ticks by culture-dependent and culture-independent methods. {\em Journal of Clinical Microbiology}. 2013, 51(2): 615-617.
[\href{http://jcm.asm.org/content/51/2/615.full}{html} ; \href{http://jcm.asm.org/content/51/2/615.full.pdf+html}{pdf}]

\item Popoola V, Tamma P, {\bf Reich NG}, Perl TM, Milstone AM. Risk Factors for Persistent MRSA Colonization in Children with Multiple Intensive Care Unit Admissions. {\em Infection Control and Hospital Epidemiology}. 2013, 34(7): 748--750.[\href{http://www.jstor.org/stable/10.1086/670994}{html}]

\item Popoola VO, Carroll KC, Ross T, {\bf Reich NG}, Perl TM and Milstone AM.  Impact of Colonization Pressure and Strain Type on MRSA Transmission in Children. {\em Clinical Infectious Diseases}. 2013, 57(10): 1458--1460. [\href{http://cid.oxfordjournals.org/content/57/10/1458.full}{html} ; \href{http://cid.oxfordjournals.org/content/57/10/1458.full.pdf}{pdf}]

\item Rock C, Harris AD, {\bf Reich NG}, Johnson JK, Thom KA. Is hand hygiene before donning non-sterile gloves in the ICU a waste of health care worker time? A randomized controlled trial. {\em American Journal of Infection Control}. 2013, 41(11): 994--996. [\href{http://www.sciencedirect.com/science/article/pii/S0196655313008481}{html} ; \href{http://www.sciencedirect.com/science/article/pii/S0196655313008481/pdfft?md5=33326b1ec41c193defddcc75deeae6e6&pid=1-s2.0-S0196655313008481-main.pdf}{pdf}]


%\hspace*{-.8cm} {\bf 2012}

\item {\bf Reich NG}, Myers JA, Obeng D, Milstone AM, Perl TM.  Empirical power and sample size calculations for cluster-randomized and cluster-randomized crossover studies. {\em PLoS ONE} 2012, 7(4): e35564. 
[\href{http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0035564}{html} ; \href{http://www.plosone.org/article/fetchObjectAttachment.action?uri=info%3Adoi%2F10.1371%2Fjournal.pone.0035564&representation=PDF}{pdf}]

\item {\bf Reich NG}, Lessler J, Cummings DAT, Brookmeyer R.  Estimating absolute and relative case fatality ratios from infectious disease surveillance data. {\em Biometrics}. 2012, 68(2): 598-606. [\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1541-0420.2011.01709.x/full}{html} ; \href{http://onlinelibrary.wiley.com/doi/10.1111/j.1541-0420.2011.01709.x/pdf}{pdf}]%

\item Elfawal M, Towler MJ, {\bf Reich NG}, Golenbock D, Weathers PJ, Rich SM. ÒDried Whole Plant Artemisia annua as an Antimalarial Therapy.Ó {\em PLoS ONE}. 2012, 7(12): e52746. [\href{http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0052746
}{html} ; \href{http://www.plosone.org/article/fetchObjectAttachment.action;jsessionid=159075642D14E1588AD000AF56745B6F?uri=info%3Adoi%2F10.1371%2Fjournal.pone.0052746&representation=PDF}{pdf}]%

\item Huntington I, Shrestha S, {\bf Reich NG}, Hagopian A. Career intentions of Nepali medical students: A survey-based cross-sectional study. {\em Health Policy and Planning}. 2012, 27(5): 417-428. [\href{http://heapol.oxfordjournals.org/cgi/content/full/czr052?ijkey=U6HzQSKw9pIhoAh&keytype=ref}{html} ; \href{http://heapol.oxfordjournals.org/content/early/2011/08/30/heapol.czr052.full.pdf?keytype=ref&ijkey=U6HzQSKw9pIhoAh}{pdf}]

%\clearpage


%\hspace*{-.8cm} {\bf 2011}

%[\href{}{html} ; \href{}{pdf}]

\item {\bf Reich NG}, Lessler J, Perl TM, Cummings DAT. Visualizing clinical evidence: citation networks for the incubation periods of respiratory viral infections. {\em PLoS ONE}. 2011, 6(4): e19496.
[\href{http://dx.plos.org/10.1371/journal.pone.0019496}{html} ; \href{http://www.plosone.org/article/fetchObjectAttachment.action?uri=info%3Adoi%2F10.1371%2Fjournal.pone.0019496&representation=PDF}{pdf}]

\item An M, {\bf Reich NG}, Crawford SO, Brookmeyer R, Louis TA, Nelson KE. Stochastic simulation of a blood product donation environment with demand spikes and supply shocks. {\em PLoS ONE} 2011, 6(7): e21752. [\href{http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0021752}{html}; \href{http://www.plosone.org/article/fetchObjectAttachment.action?uri=info%3Adoi%2F10.1371%2Fjournal.pone.0021752&representation=PDF}{pdf}]

\item Advani S, {\bf Reich NG}, Sengupta A, Gosey L, Milstone AM.  Central Line Associated Bloodstream Infections in Hospitalized Children with Peripherally Inserted Central Venous Catheters. {\em Clinical Infectious Diseases}.  2011, 52(9): 1108-1115. 
[\href{http://cid.oxfordjournals.org/content/52/9/1108.full}{html}; \href{http://cid.oxfordjournals.org/content/52/9/1108.full.pdf}{pdf}]

%\vspace{.1in}
%\hspace*{-.8cm} {\bf 2010 and earlier}

\item {\bf Reich NG}, Lessler J, Cummings DAT, Brookmeyer R.  Estimating incubation periods with coarse data. {\em Statistics in Medicine}. 2010, 28(22): 2769--2784. [\href{http://www3.interscience.wiley.com/journal/122507367/abstract}{html};\href{http://www3.interscience.wiley.com/cgi-bin/fulltext/122507367/PDFSTART}{pdf}] %\\  *{\bf ENAR Distinguished Student Paper, 2009}

\item Lessler J, Brookmeyer R, {\bf Reich NG}, Nelson KE, Cummings DAT, Perl TM.  Identifying Probable Sources of Infection for Respiratory Viruses. {\em Infection Control and Hospital Epidemiology}. 2010, 31(8): 809-15. [\href{http://www.journals.uchicago.edu/doi/full/10.1086/655023}{html};\href{http://www.journals.uchicago.edu/doi/pdf/10.1086/655023}{pdf}]

\item Lessler J, {\bf Reich NG}, Cummings DAT and The DOHMH Swine Influenza Investigation Team. Outbreak of 2009 Pandemic Influenza A (H1N1) at a New York City School. {\em New England Journal of Medicine}. 2009, 361(27): 2628-2636. [\href{http://content.nejm.org/cgi/content/full/361/27/2628}{html};\href{http://content.nejm.org/cgi/reprint/361/27/2628.pdf}{pdf}]

\item Lessler J, {\bf Reich NG}, Brookmeyer R, Perl TM, Nelson KE, Cummings DAT.  A systematic review of the incubation periods of acute respiratory viral infections. {\em Lancet Infectious Diseases}.  2009, 9(5): 291--300. [\href{http://www.thelancet.com/journals/laninf/article/PIIS1473309909700696/abstract}{html};\href{http://download.thelancet.com/pdfs/journals/laninf/PIIS1473309909700696.pdf}{pdf}]

\item Crawford SO, {\bf Reich NG}, An M, Brookmeyer R, Louis TA, Nelson KE, Notari EP, Trouern-Trend J, and Zou S. Regional and temporal variation in American Red Cross blood donations, 1995--2005.  {\em Transfusion}. 2009, 48: 1576-1583. [\href{http://www3.interscience.wiley.com/journal/120121369/abstract}{html};\href{http://www3.interscience.wiley.com/cgi-bin/fulltext/120121369/PDFSTART}{pdf}]

\end{etaremune}

%\clearpage

\vspace{.2in} 
 \begin{center} 
   \large \bf {COMMENTARIES, LETTERS \& REVIEWS}
 \end{center}

\begin{etaremune}

%\item Cummings DAT, {\bf Reich NG}. Study design to evaluate interventions against infectious diseases: the role of cluster randomization. [submitted]

\item \ul{McAndrew T}, \ul{Wattanachit N}, \ul{Gibson GC}, {\bf Reich NG}. Aggregating predictions from experts: a scoping review of statistical methods, experiments, and applications. {\em WIRES Comp Stat}. 2020. [\href{https://arxiv.org/abs/1912.11409}{preprint}; \href{https://doi.org/10.1002/wics.1514}{html}] 

\item Pollett S, Johansson MA, Biggerstaff M, Morton L, Bazaco S, Major DB, Stewart-Ibarra A,  Pavlin J, Mate S, Sippy R, Hartman L, {\bf Reich NG}, Berry IM, Chretien JP, Althouse B, Meyer D, Viboud C, Rivers C. Identification and evaluation of epidemic prediction and forecasting reporting guidelines: a systematic review and a call for action. {\em Epidemics.} 2020. (in press) [ \href{https://doi.org/10.1016/j.epidem.2020.100400}{html} ]


\item Biggerstaff M, Dahlgren FS, Fitzner J, George D, Hammond A, Hall I, Haw D, Imai N, Johansson MA, Kramer S, McCaw JM, Moss R, Pebody R, Read JM, Reed C, {\bf Reich NG}, Riley S, Vandemaele K, Viboud C, Wu JT.
Coordinating the real-time use of global influenza activity data for better public health planning.
{\em Influenza and Other Respiratory Viruses}. 2020. 14(2): 105-110. [ \href{https://doi.org/10.1111/irv.12705}{html} ]

\item \ul{Kazemi A}, \ul{Kennedy C}, \ul{Silverman G}, {\bf Reich NG}.  Opioids in the USA: Disparities in addiction and incarceration. {\em Significance}. 2019. 16(5):6-7.  
{\bf * Invited contribution for the first-place team in the 2018 ASA Public Health Data Challenge} [ \href{https://doi.org/10.1111/j.1740-9713.2019.01312.x}{html} ]

\item {\bf Reich NG}, Osthus D, Ray EL, Yamana TK, Biggerstaff M, Johansson MA, Rosenfeld R, and Shaman J.
Reply to Bracher: Scoring probabilistic forecasts to maximize public health interpretability.
{\em PNAS}. 2019.
[ \href{https://www.pnas.org/content/early/2019/09/25/1912694116}{html} ]
{\bf *Invited response to letter to editor.}

\item George DB, Taylor W, Shaman J, Rivers C, Paul B, O'Toole T, Johansson MA, Hirschman L, Biggerstaff M, Asher J, {\bf Reich NG}. 
Technology to advance infectious disease forecasting for outbreak management.
{\em Nat Comm}. 2019. 10(3932). [ \href{https://doi.org/10.1038/s41467-019-11901-7}{html} ]

\item Rivers C, Chretien JP, Riley S, Pavlin J, Woodward A, Brett-Major D, Berry IB, Morton L, Jarman RG, Biggerstaff M, Johansson MA, {\bf Reich NG}, Meyer D, Snyder MR, Pollett S. Using ``outbreak science'' to strengthen the use of models during epidemics. {\em Nat Comm}. 2019. 10(3932). [ \href{https://doi.org/10.1038/s41467-019-11067-2}{html} ]

\item Johansson MA, {\bf Reich NG}, Myers LA, Lipsitch M. Preprints: An underutilized mechanism to accelerate outbreak science. {\em PLOS Medicine}. 2018, 15(4) : e1002549. [ \href{https://doi.org/10.1371/journal.pmed.1002549}{html} ]

\item {\bf Reich NG}, Milstone AM. Improving efficiency in cluster-randomized study design and implementation: taking advantage of a crossover. {\em Open Access Journal of Clinical Trials}. 2014, 6: 11-15.
[\href{http://www.dovepress.com/getfile.php?fileID=18523}{pdf}]

\item Shardell M, {\bf Reich NG}, Perencevich EN. Commentary: Back to the future with Sir Bradford Hill: statistical analysis with hospital-acquired infections. {\em International Journal of Epidemiology}. 2013, 42(5): 1509-1510.
[\href{http://ije.oxfordjournals.org/content/early/2013/09/14/ije.dyt166.full}{html} ; \href{http://ije.oxfordjournals.org/content/early/2013/09/14/ije.dyt166.full.pdf+html}{pdf}]

\item Bessesen MT, Savor-Price C, Simberkoff M, {\bf Reich NG}, Pavia AT, Radonovich LJ. 95 Respirators or Surgical Masks to Protect Healthcare Workers Against Respiratory Infections: Are We There Yet? {\em American Journal of Respiratory and Critical Care Medicine}. 2013, 187(9): 904-905. [\href{http://www.atsjournals.org/doi/full/10.1164/rccm.201303-0581ED}{html} ; \href{http://www.atsjournals.org/doi/pdf/10.1164/rccm.201303-0581ED}{pdf}]

\item {\bf Reich NG}, Lessler J, Chu H, Cole S.  Commentary: Identification of the asymptomatic ratio. {\em Epidemiology}. 2011, 22(3): 333-335.
[\href{http://journals.lww.com/epidem/Fulltext/2011/05000/Identification_of_the_Asymptomatic_Ratio.12.aspx}{html}]


\end{etaremune}


\vspace{.2in} 
 \begin{center} 
   \large \bf {BOOK CHAPTERS}
 \end{center}

\begin{etaremune}

\item \ul{Lauer SA}, \ul{Brown AC}, {\bf Reich NG}.  ``Infectious Disease Forecasting for Public Health.''
(to appear in {\em Population biology of vector borne diseases}, edited by John M. Drake, Michael Strand, and Michael Bonsall.) 
[\href{https://arxiv.org/abs/2006.00073}{preprint}]

\end{etaremune}


\vspace{.2in} 
 \begin{center} 
   \large \bf {PUBLISHED DATA RESOURCES \& WEB APPS}
 \end{center}

\begin{etaremune}

\item {\bf Reich NG} et al. COVID-19 Forecast Hub. March 2020. \href{https://covid19forecasthub.org/}{https://covid19forecasthub.org/}

\item Cornell M, {\bf Reich NG}. Zoltar: a forecast archive. July 2019. \href{https://zoltardata.com}{https://zoltardata.com}

\item Tushar A, {\bf Reich NG}. FluSight. November 2016. \href{http://dx.doi.org/10.5281/zenodo.192509}{http://dx.doi.org/10.5281/zenodo.192509}.

\item {\bf Reich NG}. Determining Durations for Active Monitoring. July 2016. \\\href{http://iddynamics.jhsph.edu/apps/shiny/activemonitr/}{http://iddynamics.jhsph.edu/apps/shiny/activemonitr/}.

\item  CDCepi, Johansson MA, {\bf Reich NG}, Rivers C, Yu Z, Chen D. zika: Data repository of publicly available Zika data. February 2016. \href{http://dx.doi.org/10.5281/zenodo.46717}{http://dx.doi.org/10.5281/zenodo.46717}

\item {\bf Reich NG}, Ray EL. Predictions from CDC influenza prediction competition, 2015-2016. March 2016. \href{10.5281/zenodo.46840 }{http://dx.doi.org/10.5281/zenodo.46840}.

\item Lauer SA, {\bf Reich NG}. The ALERT Algorithm. November 2014. \href{http://iddynamics.jhsph.edu/apps/shiny/ALERT/}{http://iddynamics.jhsph.edu/apps/shiny/ALERT/}.

\end{etaremune}




\vspace{.3in} 
 \begin{center} 
   \pdfbookmark{FUNDING}{FUNDING}   
   \large \bf {GRANTS AND CONTRACTS}
 \end{center}
 
%\hfill {\footnotesize Dollar amounts represent total costs requested.}

\noindent
CDC, Influenza Forecasting Center of Excellence (\$3m Est. Total Costs) \hfill  Sept 2019 - Aug 2024 \\
{\normalsize {\em  Influenza Forecasting Center of Excellence at University of Massachusetts Amherst}}\\
PI: Reich. This is a cooperative agreement with CDC, advertised to fund 5 years at \$750K per year. First year was awarded for \$600K. Only two centers were funded. 
 \\

\noindent
CDC, COVID-19 Forecasting Supplement (\$350K Total Costs) \hfill  May 2020 - Aug 2020 \\
{\normalsize {\em  COVID-19 Supplemental Funding}}\\
PI: Reich. This is a supplemental contract to the Center of Excellence to support COVID-19 forecasting work.
 \\

\noindent
NIH, R35 research grant (\$1.9m Total Costs) \hfill  Sept 2016 - Aug 2021 \\
{\normalsize {\em  Statistical methods for real-time forecasts of infectious disease: dynamic time-series and machine learning approaches}}\\
PI: Reich. The R35 mechanism is the NIGMS-sponsored Maximizing Investigators' Research Award. \\

\noindent
NIH, R35 research supplement (\$315K Total Costs) \hfill  May 2020 - Aug 2021 \\
{\normalsize {\em  Statistical methods for real-time forecasts of infectious disease: expanding dynamic time-series and machine learning approaches for pandemic scenarios}}\\
PI: Reich. Supplemental funding for R35 grant to support COVID-19 forecast modeling. \\ Co-Is: Dr. Andrew Lover (UMass Epidemiology), Dr. Dan Sheldon (UMass CS).\\

\noindent
NIGMS, U24 (effort covered under R35)  \hfill April 2019 - March 2024\\
{\normalsize {\em MIDAS Coordinating Center }} \\ 
The Goal of the MIDAS Coordinating Center is to increase the use of MIDAS resources for new research and discovery. Dr. Reich serves as a Co-I on the project, with effort supported by his R35.\\
PI: Wilbert van Pahuis (UPitt). \\Co-Is: {\bf NG Reich} (UMass), Dr Elizabeth Halloran (UWash), Dr. Lauren Meyers (UT Austin).\\

\noindent
DARPA, Young Faculty Award (\$590K TC) \hfill Sept 2016 - Jan 2020 \\
{\em  Optimal Infectious Disease Prediction with Multi-Scale Ensemble Models}\\
PI: Reich. \\

\noindent
NIH, R21 research grant (\$450K TC) \hfill Dec 2014 -- Nov 2016 \\
{\em  Inference for interacting pathogens with mechanistic and phenomenological models}.\\
PI: Reich\\

\noindent
NIH, R01 research grant (\$2.5m TC) \hfill Feb 2013 -- Jan 2018 \\
{\em Methods for reducing spatial uncertainty and bias in disease surveillance}.\\
PI: Justin Lessler (JHSPH). Co-Is: Reich, Derek Cummings (JHSPH), Sopon Iamsirithaworn (Thailand MoPH). Lessler, Reich, and Cummings contribute equally to modeling efforts on this grant. \\ Reich is PI of subcontract (\$650K TC, 25\% of total). \\

\noindent
CDC/VA, IPA contract (\$200K TC) \hfill Sept 2011 -- Aug 2018\\
{\em The Respiratory Protection Effectiveness Clinical Trial (The ResPECT Study).} \\
PIs of ResPECT: Trish Perl (Johns Hopkins) and Lew Radonovich (Gainesville VA). \\
PI of subcontract to VA: Reich. He serves as the Senior Biostatistician for this cluster-randomized  trial.\\

\noindent
NSF, PESO (\$590K TC) \hfill Sept 2012 -- Aug 2015 \\
{\em Materials and Multivariable Models to Predict Tissue Tropism in Metastasis.}\\
PI: Shelly Peyton, co-PI: Reich. Reich responsible for 100\% of the statistical modeling effort (10\% of award).\\

\noindent
NIH, R21 research grant (\$390K TC) \hfill Aug 2012 -  May 2014\\
{\em Premenstrual syndrome and subsequent hypertension.}\\  
PI: Dr. Elizabeth Bertone-Johnson. co-I: Reich.  





%\clearpage 

\vspace{.3in} 
 \begin{center} 
   \pdfbookmark{TEACHING}{TEACHING}   
   \large \bf {CLASSROOM INSTRUCTION}
 \end{center}
%\noindent
%Accolades received in nomination for JHSPH TA Recognition Award, 2009\\
%\begin{tabular}{l}
%``...\em Nick goes out of his way to explain the problems in ways that are accessible and clear for people...''\\
%``...\em When Nick teaches the room is consistently full...''\\
%\end{tabular}

\noindent
Categorical Data Analysis (BIOSTATS 743) \\
\begin{tabular}{p{1in}p{5.2in}}
Fall '17, '18        & Graduate-level course (3 credits). [\href{https://nickreich.github.io/cda/}{course website}]
\end{tabular}

\vspace{.2in}

\noindent
Biostat Methods 2: Applied Regression Modeling (BIOSTATS 690NR) \\
\begin{tabular}{p{1in}p{5.2in}}
Spring '14 - '16        & Graduate-level course in linear regression (3 credits). Core requirement for Biostatistics graduate students. [\href{http://nickreich.github.io/applied-regression-2015/}{course website}]
\end{tabular}

\vspace{.2in}

\noindent
Telling Stories with Data: Statistics, Modeling, and Visualization (PUBHLTH 490ST) \\
\begin{tabular}{p{1in}p{5.2in}}
Spr '16, \ \ \ \ \ \ \ \ \ \  Fall '16-'18        & Undergraduate-level course in linear regression and data visualization (3 credits). [\href{http://nickreich.github.io/data-stories/}{course website}]
\end{tabular}

\vspace{.2in}

\noindent
Introduction to Statistical Computing using R (BIOSTATS 597D) \\
\begin{tabular}{p{1in}p{5.2in}}
Fall 2014        & Graduate introductory course in statistical computing (1 credit). %[\href{http://nickreich.github.io/statComp2014/}{course website}]
\end{tabular}

\vspace{.2in} 
\noindent
Introduction to Statistical Computing and Data Visualization (BIOSTATS 590F)\\
\begin{tabular}{p{1in}p{5.2in}}
Fall 2012        & Sponsored by the Open Education Initiative at UMass, this course was being designed to introduce upper-level undergraduate and graduate students to the world of open-source computing for public health and other scientific research. This course was taught as a hands-on, project-based data analysis workshop.
\end{tabular}

%\clearpage
 
\vspace{.2in} 
 \begin{center} 
   \pdfbookmark{MENTORSHIP}{MENTORSHIP}  
   \large \bf {MENTORSHIP \& ADVISING}
 \end{center}

\noindent {\footnotesize First placement after training in the lab indicated after names, when known.}


\vspace{.05in}
\noindent {\bf Post-doctoral fellows}\\
Tom McAndrew, 2018-2020: tenure-track faculty at Lehigh\\
Alexandria Brown, 2015-2018: research scientist at UMass\\
Evan Ray, 2015-2017: tenure-track faculty at Mt Holyoke College\\
Krzysztof Sakrejda, 2015-2017: post-doctoral research fellow at UMass \\

\noindent {\bf PhD thesis advisees}\\
Stephen Lauer, Biostatistics PhD, 2014-2019: post-doctoral research fellow at Johns Hopkins SPH \\
Xi Meng, Biostatistics PhD, 2015-present\\
Graham Casey Gibson, Biostatistics PhD, 2017-present\\
Nutcha Wattanachit, Biostatistics PhD, 2018-present\\

\noindent {\bf MS thesis advisees}\\
Justin Baldwin, Biostatistics MS, 2016-2017: Fulbright Scholar\\
Coco Kusiak, Biostatistics MS, 2017-2018: employed by Google Verily\\

\noindent {\bf Undergraduate Honors thesis advisees}\\
Kristina Yamkovoy, 2017-2018: Biostatistics PhD student, Boston University \\

\noindent {\bf MS and PhD thesis committees}\\
Jonviea Chamberlain, Epidemiology MS, 2011-2012\\
Nikki Nixon, Epidemiology MS, 2012-2013\\
Vicki McLaughlin, Epidemiology PhD, 2012-2014\\
Eric Cohen, Biostatistics MS, 2013-2014\\
Charlie Curtsinger, Computer Science PhD, 2014-2016\\
Mark Hagemann, Civil and Environmental Engineering PhD, 2015-2016\\
Alex Bogdan, Biostatistics MS, 2016: MassMutual Data Science\\
David Arbour, Computer Science PhD, 2015-2017: Facebook\\
Sangsoo Park, Kinesiology PhD, 2015-2019\\
Sra Sontisirikit, Computer Science, Asian Institute of Technology, 2015-2018 (role: expert advisor)\\
Angus Kin On Wong, Biostatistics MS, 2020\\

\noindent {\bf Graduate research assistants and programmers (not PhD advisees)}\\
Guoshu Yuan (2012-2013), Emily Ramos (fall 2014), Sangsoo Park (summer 2014), Krzysztof Sakrejda (2014-2015), Abhinav Tushar (2016-2018), Katie House (2018-2020), Yukun Li (2019), Abdul Hannan Kanji (2020), Estee Cramer (2020), Ariane Stark (2020).\\

\noindent {\bf {\href{www.statsTeachR.org}{statsTeachR.org} curriculum developers (2013-2014)}}\\
Eric Cohen, Harrel Blatt, Eric Reed, Sara Nu\~nez, Emily Ramos.\\

\noindent {\bf Undergraduate research assistants}\\
Eric Doty (Spring 2012), Courtney Yannace (Fall 2014), Harley Jean (Summer 2016 - Spring 2017), Evan Moore (Spring 2018), Justin Stott (Spring 2019), Ayush Khandelwal (Summer 2020), Dasuni Jayawardena (Summer 2020-Spring 2021).\\

\noindent{\bf Undergraduate Interns}\\
\begin{tabular}{lp{5.2in}}
Summer 2017 \  \   & Lily Rithichoo (Mt Holyoke) \\
Winter 2017 \  \   & Jordan Aron, Dean Gladish, Will Thomspon (Carleton College)  \\
Summer 2018 \  \   & Rebecca Silva (Amherst College), Willow Crawford-Crudell (Smith College), Dean Gladish (Carleton College)  \\
\end{tabular}


\vspace{.2in} 
 \begin{center} 
   \large \bf {WORKSHOPS \& DATAFESTS}
 \end{center}

\noindent
Five College DataFest (Amherst, MA) \\
\begin{tabular}{p{1in}p{5.2in}}
2014-19        & UMass team coordinator: responsible for recruiting teams of undergraduate students to compete in weekend-long data competition. [ \href{http://www.science.smith.edu/datafest/}{datafest website} ]
\end{tabular}

\vspace{.1in} 

\noindent
HackHer413 (Amherst, MA) \\
\begin{tabular}{p{1in}p{5.2in}}
February 2019        & Data Science Judge for all women and non-binary student hackathon. [ \href{https://www.hackher413.com/}{website} ]
\end{tabular}


\vspace{.1in} 
\noindent
HackEbola (UMass-Amherst) \\
\begin{tabular}{p{1in}p{5.2in}}
November 2014        & Co-organized three-day \href{http://gridclub.io/hackebola-umass-amherst-projects}{HackEbola hackathon/datafest} at UMass with Graduate Researchers interested in Data student group.
\end{tabular}

\vspace{.1in} 
\noindent
Data Sciences for the Life Sciences in a High Performance Computing Environment (Holyoke, MA) \\
\begin{tabular}{p{1in}p{5.2in}}
February 2014        & Directed and taught a one-day hands-on high-performance statistical computing workshop for researchers. Workshop held at the \href{http://www.mghpcc.org/}{MGHPCC}.
\end{tabular}


\vspace{.1in} 
\noindent
Data Analysis and Visualization using R, Social and Demographic Research Institute (UMass) \\
\begin{tabular}{p{1in}p{5.2in}}
July 2012        & Designed and taught a two-day hands-on data analysis workshop for researchers.
\end{tabular}


\vspace{.1in} 
\noindent
Outbreak investigation workshops, Thai Ministry of Public Health (Bangkok, Thailand)\\
\begin{tabular}{p{1in}p{5.2in}}
March 2009 and  March 2012        & Designed and taught a three-day workshop on statistical modeling of outbreaks for field epidemiologists with Justin Lessler from the Johns Hopkins Epidemiology Dept.  The workshop was sponsored by the NIH Fogarty International Center.
\end{tabular}


%\vspace{.2in} 
%\noindent
%Department of Biostatistics, Johns Hopkins Bloomberg School of Public Health (2006--2010)\\
%\begin{tabular}{p{1in}p{5.2in}}
%9 semesters & teaching assistant for graduate-level Intro Biostatistics \\ 
%3 semesters & statistical advisor for M.P.H. students working on capstone projects\\
%1 semester  & teaching assistant for undergraduate-level Intro Biostatistics
%2009 (Fall)         & Teaching Assistant for Methods in Biostatistics I and II\\
%2007--2008 (Fall)   & Lead Teaching Assistant for Statistical Methods in Public Health I and II\\
%2007--2009 (Spring) & Biostatistics Teaching Assistant for M.P.H. capstone project \\
%2007, 2010 (Spring) & Teaching Assistant for Statistical Methods in Public Health III and IV\\
%2006 (Fall)         & Teaching Assistant for Biostatistics in Public Health (undergraduate intro) \\
%\end{tabular}

%\vspace{.2in} 
%\noindent
%Department of Biostatistics, Boston University School of Public Health (2005)\\
%\begin{tabular}{p{1in}p{5.2in}}
%1 semester & Lead TA for Introduction to Biostatistics \\
%\end{tabular}

%\clearpage

\vspace{.2in} 
 \begin{center} 
    \pdfbookmark{COMPUTING}{COMPUTING}  
    \large \bf {SOFTWARE \& COMPUTING}
 \end{center}
General software development from Reich Lab: see \href{http://reichlab.io/research#03-software}{lab webpage}.\\
R package development: \href{http://cran.r-project.org/web/packages/coarseDataTools/index.html}{coarseDataTools} and \href{http://cran.r-project.org/web/packages/clusterPower/index.html}{clusterPower}, R packages (available on CRAN) \\
Open source teaching curricula: Co-founder of \href{http://statsteachr.org}{statsTeachR.org}


%\clearpage

\vspace{.2in} 
 \begin{center} 
   \pdfbookmark{PRESS}{PRESS}  
   \large \bf {SELECTED PRESS \& MEDIA COVERAGE}
 \end{center}
 
\noindent Links to press coverage of the COVID-19 Forecast Hub are available \href{https://covid19forecasthub.org/doc/media/}{here}.

\noindent Links to press coverage of the COVID-19 Expert Surveys project are available \href{https://github.com/tomcm39/COVID19_expert_survey}{here}.

\noindent \href{https://apnews.com/afs:Content:9213894577}{``COVID-19 pandemic is not 'fading' in the United States''}. {\em Associated Press}. 6 August 2020.

\noindent \href{https://www.washingtonpost.com/politics/2020/08/05/health-202-why-individual-models-coronavirus-deaths-are-often-wrong/}{``The Health 202: Why individual models of coronavirus deaths are often wrong''}. {\em Washington Post}. 5 August 2020.

\noindent \href{https://iqt.podbean.com/e/how-disease-modeling-can-help-inform-public-health-decision-making-with-dr-nick-reich/}{``How Disease Modeling Can Help Inform Public Health Decision Making, with Dr. Nick Reich''}. {\em The IQT Podcast}. 4 August 2020.

\noindent \href{https://nhtalkradio.com/?p=14310}{``Off The Record with Paul Hodes''}. New Hampshire Talk Radio. 17 July 2020.

\noindent \href{https://www.wcvb.com/article/umass-model-projects-833-more-covid-19-deaths-in-state-by-4th-of-july/32819172#}{``UMass model projects 833 more COVID-19 deaths in state by 4th of July}. {\em WCVB, Channel 5, ABC}. 9 June 2020.

\noindent \href{https://www.economist.com/graphic-detail/2020/05/23/early-projections-of-covid-19-in-america-underestimated-its-severity}{``Early projections of covid-19 in America underestimated its severity''}. {\em The Economist}. 23 May 2020.

\noindent \href{https://www.pbs.org/newshour/show/what-computer-based-models-can-tell-us-about-coronavirus-and-what-they-cant}{``What computer-based models can tell us about coronavirus-and what they can't''}. {\em PBS NewsHour}. 20 May 2020.

\noindent \href{https://www.wgbh.org/news/local-news/2020/05/20/in-it-together-5-20-2020}{``In It Together: live broadcast''}. {\em WGBH}. 20 May 2020.

\noindent \href{https://www.npr.org/sections/health-shots/2020/05/13/855038708/combining-different-models-new-coronavirus-projection-shows-110-000-deaths-by-ju}{``How To Make Sense of All The COVID-19 Projections? A New Model Combines Them''}. {\em NPR Morning Edition}. 13 May 2020.

\noindent \href{https://www.bostonglobe.com/2020/05/07/metro/umass-professor-develops-ensemble-forecast-coronavirus-pandemic-projects-103000-deaths-nationwide-by-end-may/}{``UMass professor develops ensemble forecast for coronavirus pandemic; projects 103,000 deaths nationwide by end of May''}. {\em Boston Globe}. 7 May 2020.

\noindent \href{https://www.deccanherald.com/international/world-news-politics/us-milestone-of-100000-coronavirus-deaths-likely-by-june-833657.html}{``US milestone of 100,000 coronavirus deaths likely by June''}. {\em Agence France Press}. 5 May 2020.

\noindent \href{https://projects.fivethirtyeight.com/covid-forecasts/}{``Where The Latest COVID-19 Models Think We're Headed ? And Why They Disagree''}. {\em FiveThirtyEight}. 1 May 2020.

\noindent \href{https://www.wgbh.org/news/local-news/2020/04/27/in-it-together-4-27-2020}{``In It Together: live broadcast''}. {\em WGBH}. 27 April 2020.

\noindent \href{https://www.sciencemag.org/news/2020/04/surveys-infectious-disease-experts-aim-predict-covid-19-s-toll}{``Surveys of infectious disease experts aim to predict COVID-19's toll''}. {\em Science News}. 23 April 2020. 

\noindent \href{https://www.nytimes.com/interactive/2020/04/22/upshot/coronavirus-models.html}{``What 5 Coronavirus Models Say the Next Month Will Look Like''}. {\em NY Times}. 22 April 2020.

\noindent \href{https://mashable.com/article/did-i-have-coronavirus/}{``'Did I already have coronavirus?': People wonder if they previously had COVID-19, but the answer isn't easy''}. {\em Mashable}. 8 April 2020.

\noindent \href{https://www.miamiherald.com/news/coronavirus/article241784446.html}{``'Flu-like' data might help track coronavirus spread. Why did Florida stop publishing it?''}. {\em Miami Herald}. 7 April 2020.

\noindent \href{https://www.economist.com/briefing/2020/04/04/the-hard-choices-covid-policymakers-face}{"The hard choices covid policymakers face"}. {\em The Economist}. 4 April 2020.

\noindent \href{https://www.rollingstone.com/politics/politics-news/infectious-disease-experts-coronavirus-poll-965759/}{``Here?s How More Than 20 Infectious-Disease Experts See Coronavirus Playing Out in the U.S.''} {\em Rolling Stone}. 19 March 2020.

\noindent \href{https://gizmodo.com/real-number-of-u-s-coronavirus-cases-could-be-as-high-1842411303}{``Real Number of U.S. Coronavirus Cases Could Be as High as 150,000, New Estimates Suggest''}. {\em Gizmodo}. 19 March 2020.

\noindent
\href{https://www.wwlp.com/news/local-news/hampshire-county/umass-professor-to-receive-3m-from-cdc-to-help-predict-flu-outbreaks/}{``UMass professor to receive \$3M from CDC to help predict flu outbreaks''} {\em WWLP Channel 22}. 9 Oct 2019.

\noindent
\href{https://www.gazettenet.com/FluCenter-hg-101019-29221119}{``Flu tracker: UMass biostatistician lands \$3M to forecast flu''} {\em Daily Hampshire Gazette}. 9 Oct 2019.

\noindent
\href{https://www.nepr.net/post/umass-researcher-gets-cdc-money-forecast-flu-better}{``UMass Researcher Gets CDC Money To Forecast The Flu Better''} {\em New England Public Radio}. 8 Oct 2019.


\noindent
\href{https://www.nature.com/articles/d41586-019-02755-6}{``Real-time flu tracking''} {\em Nature Outlook}. 18 Sep 2019.

\noindent
\href{https://www.nepr.net/post/under-weather-new-flu-forecast-aims-predict-activity#stream/0}{``Under The Weather? New Flu 'Forecast' Aims To Predict Activity''} {\em NEPR}. 28 Jan 2019.

\noindent
\href{http://www.wcvb.com/article/flu-season-escalating-earlier-than-normal/15056566}{``Flu season escalating earlier than normal''} {\em WCVB (TV interview)}. 10 Jan 2018.

\noindent
\href{http://www.bostonglobe.com/metro/2018/01/01/umass-researcher-helps-predict-timing-peak-flu/Jv8HYKaJH3qYY0q8dQ8X8J/story.html}{``UMass researcher helps predict the timing and the peak of the flu'} {\em Boston Globe}. 2 Jan 2018.

\noindent
\href{http://www.gazettenet.com/home/15612683-95/nicholas-g-reich-krzysztof-sakrejda-criticizes-gazette-measles-headline-for-down-playing-risks}{``Letter to editor: critical of measles headline for down-playing risks''} {\em Daily Hampshire Gazette}. 11 Feb 2015.

\noindent
\href{http://nepr.net/news/2014/11/24/flu-season-made-easy-with-new-tool/}{``Flu Season Made Easy With New Tool.''} {\em New England Public Radio}. 24 Nov 2014.

\noindent
\href{http://www.gazettenet.com/home/14466582-95/hackebola-at-umass-seeks-to-aid-fight-against-epidemic-in-west-africa}{``HackEbola at UMass aids fight against West African epidemic ''} {\em Daily Hampshire Gazette}. 22 Nov 2014.

\noindent
\href{http://www.nytimes.com/2013/07/09/health/understanding-the-protective-side-of-dengue-virus.html}{``Understanding the Protective Side of Dengue Virus.''} {\em New York Times}. 9 July 2013.


\vspace{.2in} 
 \begin{center} 
   \pdfbookmark{INVITED TALKS}{INVITED TALKS}  
   \large \bf {INVITED TALKS}
 \end{center}
 \begin{enumerate}
 
\item {\bf Keynote Address:} 2nd International Workshop on Forecasting for Social Good. Bordeaux, France. 1 July 2021. (postponed from 2020) [ \href{https://www.f4sg.org/}{website} ]

\item {\bf Keynote Session Invited Speaker:} 6th Seattle Symposium in Biostatistics: Precision Health in the Age of Data Science. 24 Nov 2020. [ \href{https://www.biostat.washington.edu/news/calendar/symposium}{website} ]

\item {\bf Keynote Address:} ``Methods and motives for infectious disease models -- the tale of COVID-19.'' ASTMH Committee on Global Health Pre-Meeting Course: Modeling for Disease Outbreaks, Practical Approaches to Understanding and Using Models. 11 Nov 2020.

\item {\bf Plenary session panelist:} COVID-19 panel. INFORMS Virtual Annual Meeting. 9 Nov 2020.

\item {\bf Keynote Address:} 1st ACM SIGSPATIAL International Workshop on Modeling and Understanding the Spread of COVID-19. In conjunction with the ACM SIGSPATIAL 2020 conference. 3 Nov 2020.  

\item {\bf Invited Panelist and Session Chair:}  COVID-19 Forecasting. International Symposium on Forecasting: Virtual ISF 2020. 26 Oct 2020.

\item ``Data Science Zoominar: COVID-19 Prediction Models.'' Harvard University Dana Farber Cancer Institute, Department of Data Science. 21 July 2020. [ \href{https://www.youtube.com/watch?v=rnpgtWywRcU}{YouTube} ]

\item ``The COVID-19 Forecast Hub: using statistics and data science to support decision-making in a pandemic.'' American Statistical Association and Journal of Data Science Webinar Series: Data Science in Action in Response to the Outbreak of COVID-19. UConn. 17 July 2020. [ \href{https://uconn-cmr.webex.com/uconn-cmr/lsr.php?RCID=1c31b59b21e34d5bb5f5d29a11c70bf7}{video} ]

\item ``The Computational Science of Real-time Influenza Forecasting.'' Friedrich-Alexander-Universit\"at Erlangen-N\"urnberg (FAU), Erlangen, Germany. 26 November 2019.

\item ``Statistical considerations for probabilistic ensemble forecasts of infectious disease outbreaks.'' Seminar for the Center of Mathematics in Sciences, Engineering, and Economics, Karlsruher Institut f\"ur Technologie (KIT), Karlsruhe, Germany. 22 October 2019.

\item ``The Computational Science of Real-time Influenza Forecasting.'' Heidelberg Institute for Theoretical Studies (HITS) Colloquium, Heidelberg, Germany. 21 October 2019. [ \href{https://www.youtube.com/watch?v=hSTzv9Z8sfU}{YouTube} ]

\item ``Collaborative Influenza Forecasting in the US.'' 7th Annual Conference to Increase Diversity in Mathematical Modeling and Public Health, Harvard University, Boston, MA. 30 November 2018.

\item ``Forecasting infectious disease epidemics via weighted density ensembles.'' Z\"uKoSt: Seminar on Applied Statistics, ETH Z\"urich, Switzerland. 17 May 2018.

\item ``Forecasting infectious disease epidemics via weighted density ensembles.'' LMU Statistics Colloquium, Munich, Germany. 14 May 2018.

\item ``Building a Collaborative Ensemble to Forecast Influenza in the US.'' MIDAS Network Meetings, Bethesda, MD. 3 April 2018.

\item ``Forecasting Infectious Disease Transmission.'' Symposium on the Population Biology of Vector-borne Diseases, Center for the Ecology of Infectious Diseases, University of Georgia, Athens, GA. 24 February 2018.

\item ``Algorithm Soup: Improving Influenza Forecasting in the US using Ensemble Learning.'' COBRE Center for Computational Biology of Human Disease Seminar Series, Brown University, Providence, RI. 24 January 2018. 

\item ``Collaborative Influenza Forecasting in the U.S.'' WHO Influenza Incidence Analytics Group. Virtual presentation. 20 December 2017. 

\item ``Comparison of ensemble methods for forecasting influenza in the United States.'' Epidemics6 Conference, Barcelona, Spain. 28 November 2017.

\item ``Forecasting Infectious Disease Outbreaks.'' UMass Molecular and Cellular Biology Seminar Series, Amherst, MA. 31 October 2017.

\item ``Forecasting Infectious Disease Outbreaks via Weighted Density Ensembles.'' Yale Public Health Modeling Concentration Seminar Series, New Haven, CT. 2 October 2017.

\item ``Building a Collaborative Ensemble to Forecast Influenza in the US.'' CDC, Atlanta, GA. 29 August 2017.

\item ``Prediction of Infectious Disease Epidemics via Weighted Density Ensembles.'' MIDAS Network Meetings, Atlanta, GA. May 2017.

\item ``Analytical approaches for illuminating Zika and Dengue transmission dynamics.'' CDC Dengue Branch, San Juan, Puerto Rico. 24 February 2017.

\item ``Real-time Prediction of Infectious Disease Outbreaks.'' Johns Hopkins Biostatistics Seminar Series, Baltimore, MD. 3 October 2016.

\item ``New Approaches for Predicting Outbreaks.'' Pandemic Prediction and Forecasting Working Group, White House Office of Science and Technology Policy, Washington DC. 9 February 2016.

\item ``Estimating Population Susceptibility in Dynamic Models of Infectious Disease.'' Boston University Biostatistics Seminar Series, Boston, MA. 14 May 2015.

\item ``Estimating Population Susceptibility in Dynamic Models of Infectious Disease.'' New England Statistics Symposium. University of Connecticut, Storrs, CT. 25 April 2015.

\item {\bf Keynote Address}: ``Predicting Dengue Fever Outbreaks in Thailand.'' Massachusetts Undergraduate Research Conference. Amherst, MA. 24 April 2015.

\item ``Estimating Population Susceptibility in Dynamic Models of Infectious Disease.'' Computational Social Science Institute Seminar Series, UMass-Amherst. Amherst, MA. 17 April 2015.

\item ``Statistical Challenges in Real-Time Infectious Disease Forecasting.'' Quantitative Methods Core Methods Seminar, UMass-Worcester Medical School. Worcester, MA. 7 April 2015.

\item ``statsTeachR: Open Resources for Teaching Statistics.'' New England Statistics Symposium.  Boston, MA. 26 April 2014.

\item ``Open Resources for Teaching Statistics.'' Department of Mathematics and Statistics, University of Massachusetts.  Amherst, MA. 7 April 2014.

\item ``Estimating case fatality ratios from infectious disease surveillance data.'' American Public Health Association Annual Conference. Boston, MA. 4 November 2013.

\item ``Estimating case fatality ratios from infectious disease surveillance data.'' Joint Conference by the International Chinese Statistical Association and the International Society for Biopharmaceutical Statistics (ICSA-ISBS), Washington DC. 10 June 2013.

\item ``Social coding with RStudio and GitHub.'' Pioneer Valley and Five College R Statistical Meetup. 13 February 2013.

\item ``Drawing inference about interactions between pathogens in infectious disease systems.'' Department of Mathematics and Statistics, University of Massachusetts. 26 March 2012.

\item  ``Making inferences about infection using the incubation period.'' Center for Quality of Care Research, Baystate Medical Center. Springfield, MA. 16 November 2011.

\item  ``Making inferences about infection using the incubation period.'' Department of Epidemiology and Public Health Seminar Series, University of Maryland. 21 April 2011.
%   \item Reich NG, Lessler J, Brookmeyer R.  Estimating Case Fatality Ratios from Infectious Disease Surveillance Data.  Joint Statistical Meetings.  August 4, 2010.\

%   \item Reich NG, Lessler J, Brookmeyer R.  Estimating Case Fatality Ratios from Infectious Disease Surveillance Data.  International Biometric Society's Eastern North American Region Spring Meetings.  March 23, 2010.

%   \item Reich NG, Lessler J, Cummings DAT, Brookmeyer R.  Estimating the incubation period of swine flu in real-time during an outbreak: sample size considerations. Joint Statistical Meetings.  August 4, 2009.

%   \item Reich NG, Lessler J, Cummings DAT, Brookmeyer R.  Estimating incubation periods with coarse data. International Biometric Society's Eastern North American Region Spring Meetings.  March 17, 2009.

 \end{enumerate} 
 
% \clearpage

\vspace{.2in} 
 \begin{center} 
   \pdfbookmark{GRANT REVIEW ACTIVITIES}{GRANT REVIEW ACTIVITIES}  
   \large \bf {GRANT REVIEW ACTIVITIES}
 \end{center}

\noindent
{\bf NIH ad hoc Study Section and Council Member}\\
\begin{tabular}{lp{5.2in}}
 2017 \   \      & NIGMS Advisory Council \\
 2016 \   \      & Infectious, Reproductive, Asthma and Pulmonary Conditions Study Section (IRAP) \\
 2015 \  \      & NEI Clinical and Epidemiological Applications: Uveitis, Cornea and Refractive Error
\end{tabular}


\noindent
{\bf Medical Research Council UK Peer Reviewer}\\
\begin{tabular}{lp{5.2in}}
 2016 \   \      &  Review of a single application. \\
\end{tabular}

\vspace{.1in} 



\vspace{.1in} 
 \begin{center} 
   \pdfbookmark{MEMBERSHIPS}{MEMBERSHIPS}  
   \large \bf {MEMBERSHIPS}
 \end{center}

\noindent 
%American Statistical Association, International Biometric Society (ENAR), 
%%American Public Health Association, 
%Foundation for Open Access Statistics, UMass Center for Clinical and Translational Science, American Society for Tropical Medicine and Hygiene.    
\begin{tabular}{lp{5.2in}}
2019- \  \   & International Institute of Forecasters \\
2017- \  \   & New England Statistical Society \\
2014- \  \   & Foundation for Open Access Statistics \\
2011- \  \   & UMass Center for Clinical and Translational Science \\
2008- \  \   & American Statistical Association \\
2008- \  \   & International Biometric Society (ENAR) \\
\end{tabular}
\vspace{.1in}  

%  \clearpage

\vspace{.1in} 
 \begin{center} 
   \pdfbookmark{EDITORIAL ACTIVITIES}{EDITORIAL ACTIVITIES}  
   \large \bf {EDITORIAL ACTIVITIES}
 \end{center}

\noindent
{\bf Founding Editor}, {\em PLOS Disease Forecasting and Surveillance Channel}, 2017-present\\
{\bf Statistical Advisory Board Member}, {\em PLOS Medicine}, 2016-2017\\
{\bf Review Board Member}, {\em PLOS Currents: Outbreaks}, 2015-2018\\
{\bf Editorial Board Member}, {\em PLOS ONE}, 2013-2017\\
{\bf Guest Editor}, {\em PLOS Neglected Tropical Diseases, 2016}.
\vspace{.1in} 

\begin{minipage}{\textwidth}
\noindent
{\bf Reviewer}
\vspace{.1in} 

\begin{tabular}{ll}
& {\em Science}\\
& {\em JAMA}\\
& {\em Biostatistics}\\
& {\em Statistics in Medicine}\\
& {\em American Statistician}\\
& {\em American Journal of Epidemiology} \\
& {\em International Journal of Forecasting} \\
& {\em Nature Communications} \\
& {\em PLOS Medicine}\\
& {\em PLOS Computational Biology} \\
& {\em The Lancet Infectious Diseases} \\
& {\em Epidemiology} \\
& {\em British Medical Journal} \\
& {\em PLoS Currents: Outbreaks}\\
& {\em Epidemics}\\
& {\em American Journal of Tropical Medicine and Hygiene}\\ 
& {\em Clinical Trials} \\
& {\em PeerJ}\\
& {\em Emerging Infectious Diseases}\\
& {\em Proceedings of the Royal Society B: Biological Sciences}\\ 
& {\em BMC Public Health}\\
& {\em PLOS ONE}\\ 
& {\em Scientific Reports}\\
& {\em Demography}\\ 
& {\em Medical Decision Making}\\ 
& {\em Influenza and Other Respiratory Viruses}\\ 
& {\em Environmental Health}\\ 
& {\em International Journal of Health Geographics}
\end{tabular}
\end{minipage}

%{\em American Journal of Epidemiology}, {\em Epidemiology}, {\em BMC Public Health}, {\em Proceedings of the Royal Society B: Biological Sciences}, {\em PLoS ONE}, {\em Demography}, {\em Medical Decision Making}, {\em Influenza and Other Respiratory Viruses}, {\em International Journal of Health Geographics}.  
 

 
 \clearpage

\vspace{.2in} 
 \begin{center} 
   \pdfbookmark{SERVICE}{SERVICE}  
   \large \bf {SERVICE}
 \end{center}

\vspace{.1in}
\noindent
{\bf Faculty Searches} \\
\begin{tabular}{ll}
2013-2014 & Member, Assistant Lecturer Search Committee \\
2014-2015 & Member, Open-rank Tenure Track Search Committee \\
2014-2015 & Chair, Assistant/Associate Tenure Track Search Committee \\
2016-2017 & Member, Assistant Professor Tenure Track Search Committee \\
2017-2018 & Member, Institute for Applied Life Sciences, Assistant Professor for Large Data Analytics\\ 
2017-2018 & Member, Biostatistics and Epidemiology Department Chair Search Committee\\ 
2018-2019 & Member, Assistant Professor Tenure Track Search Committee, Biostatistics\\ 
\end{tabular}

\vspace{.1in}
\noindent
{\bf Department of Biostatistics and Epidemiology, UMass School of Public Health and Health Sciences} \\
\begin{tabular}{lp{5.2in}}
2011-2012   & Co-organizer for Department's seminar series \\
2012-2013   & Co-organizer for Department's seminar series \\
                    & Chair, Biostatistics Curriculum Committee \\
2013-2014   & Member, Biostatistics Curriculum Committee \\
                    & Chair, Biostatistics Admissions and Student Outreach Committee \\
                    & Representative, Five College Statistics Program \\
2014-2015   & Member, Biostatistics Curriculum Committee \\
		   & Member, Biostatistics Admissions and Student Outreach Committee\\
                    & Representative, Five College Statistics Program \\
2015-2016   & Chair, Biostatistics Curriculum Committee \\
		   & Member, Biostatistics Admissions and Student Outreach Committee\\
		   & Chair, Biostatistics Accelerated MS program \\
                    & Representative, Five College Statistics Program \\
2016-2017   & Member, Biostatistics Curriculum Committee \\
		   & Chair, Biostatistics Admissions and Student Outreach Committee\\
		   & Chair, Biostatistics Accelerated MS program \\
		   & Representative, Five College Statistics Program \\
2017-2018   & Member, Biostatistics Curriculum Committee \\
		   & Member, Biostatistics Admissions and Student Outreach Committee\\
		   & Chair, Biostatistics Accelerated MS program \\
                    & Representative, Five College Statistics Program \\
2018-2019   & Chair, Biostatistics Admissions and Student Outreach Committee\\
		   & Chair, Biostatistics Accelerated MS program \\
		   & Member, Biostatistics Graduate Program Coordination Committee \\
                    & Representative, Five College Statistics Program \\   
2019-2020  & on sabbatical \\
2020-2021  & Chair, Biostatistics Admissions Committee \\ 
                    & Representative, Five College Statistics Program \\
\end{tabular}


\vspace{.1in}
\noindent
{\bf UMass School of Public Health and Health Sciences and campus-wide service} \\
\begin{tabular}{lp{5.2in}}
2014-2015   & Faculty Advisor, Graduate Researchers interested in Data (GRiD) student group\\
2015-2016   & Faculty Advisor, Graduate Researchers interested in Data (GRiD) student group\\
& Member, UMass IT Strategic Planning Research Committee \\
                    & Member, ad hoc Computing committee\\
2015-2016   & Faculty Advisor, Graduate Researchers interested in Data (GRiD) student group\\
& Member, ad hoc Computing committee \\
2017-2018   & Faculty Advisor, Graduate Researchers interested in Data (GRiD) student group\\
& Member, School Personnel Committee \\
2018-2019   &  Member, School Personnel Committee \\
2019-2020  & on sabbatical \\
\end{tabular}

\vspace{.1in}
\noindent
{\bf Other Professional Service} \\
\begin{tabular}{lp{5.2in}}
2013-2014   & Co-organizer, Western Mass Data Science, Stats, and R Meetup\\
                    & Chair, Biostatistics Admissions and Student Outreach Committee \\
                    & UMass Biostatistics representative, Five College Statistics Program \\
                    & Predoctoral mentor, \href{https://mathalliance.org/}{The Math Alliance for Doctoral Studies}\\
2014-2015   & Organizer, Western Mass Data Science, Stats, and R Meetup\\
		   & Member, Biostatistics Admissions and Student Outreach Committee\\
                    & UMass Biostatistics representative, Five College Statistics Program \\
                    & Predoctoral mentor, \href{https://mathalliance.org/}{The Math Alliance for Doctoral Studies}\\
2015-2016   & Organizer, Western Mass Data Science, Stats, and R Meetup\\
		   & Member, Biostatistics Admissions and Student Outreach Committee\\
		   & Chair, Biostatistics Accelerated MS program \\
                    & UMass Biostatistics representative, Five College Statistics Program \\
                    & Predoctoral mentor, \href{https://mathalliance.org/}{The Math Alliance for Doctoral Studies}\\
2016-2017   & Organizer, Western Mass Data Science, Stats, and R Meetup\\
                    & Predoctoral mentor, \href{https://mathalliance.org/}{The Math Alliance for Doctoral Studies}\\
2017-2018 & Organizer, Western Mass Data Science, Stats, and R Meetup\\
		 & Secretary and Treasurer, Five College Statistics Program\\
		 & Vice President for Scientific Program, New England Statistical Society \\
		 & Organizing Committee, 2018 New England Statistical Symposium \\ 
                  & Predoctoral mentor, \href{https://mathalliance.org/}{The Math Alliance for Doctoral Studies}\\
                  & Steering Committee Member, NIH MIDAS Network  \\
2018-2019 & Organizer, Western Mass Data Science, Stats, and R Meetup\\
		 & Chair, Five College Statistics Program\\
                  & Predoctoral mentor, \href{https://mathalliance.org/}{The Math Alliance for Doctoral Studies}\\
                  & Steering Committee Member, NIH MIDAS Network  \\
2019-2020 & co-Organizer, Royal Society Discussion meeting (London, Oct 2020): ``Forecasting natural and social systems'' and satellite meeting ``Epidemiological forecasting of
infectious disease for public health'' \\ 
		 & Member, Program Committee, useR!2020 Satellite Conference (Munich, July 2020) \\
		 & co-Chair, US CDC Coronavirus Forecasting Working Group
\end{tabular}

%\vspace{.1in}
%\noindent
%{\bf Community}\\
%\begin{tabular}{lp{5.2in}}
%2011-2012 & Coach for junior varsity high school ultimate frisbee (Amherst, MA)\\
%%2008-2009 & Technology consultant for Baltimore CarShare\\
%2003-2004 & Assistant coach with the North Oakland Little League (Oakland, CA) \\
%\end{tabular}


%\vspace{.2in} 
%\begin{center} \large \bf {ABSTRACTS} \pdfbookmark{ABSTRACTS}{ABSTRACTS}  \end{center}

%\input{abstracts}
%\newpage
\end{document}
